---
title: "Predicting cognitive performance from fMRI working memory data using the ABCD dataset"
subtitle: "Mass-univariate, OLS regression, and elastic net"
author: "Narun Pornpattananangkul, Adam Bartonicek and Yue Wang"
date: "1/10/2020"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: united
    number_sections: true
    toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```


```{r}
rm(list = ls(all.names = TRUE)) #will clear all objects includes hidden objects.
gc() #free up memrory and report the memory usage.
```

# Data Preparation

## Loading libraries

The following libraries and default settings were used during the analysis:

```{r load_libraries}
options(scipen = 999)

# if (!requireNamespace("BiocManager", quietly = TRUE))
#     install.packages("BiocManager")
# BiocManager::install("survcomp")

library(tidyverse)
library(broom)
library(eNetXplorer)
library(glmnet)
library(olsrr)
library(caret)
library(pander)
library(tidymodels)
library("cowplot")


##parallel map

#library(parallel)  
library("furrr")
future::plan(multiprocess(workers = 16))

theme_set(theme_bw() + theme(panel.grid = element_blank()))

```

## Loading the data

We first loaded all of the relevant data files (not shown here as they refer to local directories):

```{r load_data, echo=FALSE}
##qnap
dataFold = "/mnt/data/ABCD/ABCD_LVM/Tables2p01/"
manipuFold = "/mnt/data/ABCD/ABCD_LVM/Analysis/ManipulatedData/"
anotherFold = "/mnt/data/Yue script/"
```

```{r}
MRFINDINGS01 <-read.csv(paste0(dataFold, "ABCD_MRFINDINGS01_DATA_TABLE.csv")) %>% 
  filter(EVENTNAME =="baseline_year_1_arm_1") 
MRIQCRP102 <-read.csv(paste0(dataFold, "MRIQCRP102_DATA_TABLE.csv")) %>% 
  filter(EVENTNAME =="baseline_year_1_arm_1") 
MRIQCRP202 <-read.csv(paste0(dataFold, "MRIQCRP202_DATA_TABLE.csv")) %>% 
  filter(EVENTNAME =="baseline_year_1_arm_1") 
MRIQCRP302 <-read.csv(paste0(dataFold, "MRIQCRP302_DATA_TABLE.csv")) %>% 
  filter(EVENTNAME =="baseline_year_1_arm_1") 
FREESQC01 <-read.csv(paste0(dataFold, "FREESQC01_DATA_TABLE.csv")) %>% 
  filter(EVENTNAME =="baseline_year_1_arm_1") 
DMRIQC01 <-read.csv(paste0(dataFold, "DMRIQC01_DATA_TABLE.csv")) %>% 
  filter(EVENTNAME =="baseline_year_1_arm_1") 
NBackBeh <-read.csv(paste0(dataFold, "ABCD_MRINBACK02_DATA_TABLE.csv")) %>% 
  filter(EVENTNAME =="baseline_year_1_arm_1") 
NBackAparc <-read.csv(paste0(dataFold, "NBACK_BWROI02_DATA_TABLE.csv")) %>% 
  filter(EVENTNAME =="baseline_year_1_arm_1") 
NbackAsegDest <-read.csv(paste0(manipuFold, "NbackDestAsegReadableGgseg3d.csv")) 
# NbackAsegDestR1 <-read.csv(paste0(manipuFold, "NbackDestAsegReadableGgseg3dRunOne.csv"))
# NbackAsegDestR2 <-read.csv(paste0(manipuFold, "NbackDestAsegReadableGgseg3dRunTwo.csv")) 
MRIinfo <-tbl_df(read.csv(paste0(dataFold, "ABCD_MRI01_DATA_TABLE.csv"))) %>% 
  filter(EVENTNAME =="baseline_year_1_arm_1") 
Siteinfo <-tbl_df(read.csv(paste0(dataFold, "ABCD_LT01_DATA_TABLE.csv"))) %>% 
  filter(EVENTNAME =="baseline_year_1_arm_1") 
NIH_TB <-tbl_df(read.csv(paste0(dataFold,"ABCD_TBSS01_DATA_TABLE.csv"))) %>% 
  filter(EVENTNAME =="baseline_year_1_arm_1") 
LittleMan <-tbl_df(read.csv(paste0(dataFold,"LMTP201_DATA_TABLE.csv"))) %>% 
  filter(EVENTNAME =="baseline_year_1_arm_1") 
Pearson <-tbl_df(read.csv(paste0(dataFold,"ABCD_PS01_DATA_TABLE.csv"))) %>% 
  filter(EVENTNAME =="baseline_year_1_arm_1")

short_names <- tbl_df(read.csv(paste0(anotherFold,"ShortNames_all.csv") ))

MRIQcAll <- plyr::join_all(list(MRFINDINGS01,MRIQCRP102,
                          MRIQCRP202,MRIQCRP302,FREESQC01,DMRIQC01,
                          NBackBeh,NBackAparc,NbackAsegDest,MRIinfo,Siteinfo,NIH_TB,LittleMan,Pearson), 
                          by='SUBJECTKEY', type='full')

MRIQcAll <- MRIQcAll[,!duplicated(colnames(MRIQcAll))]

```

## Quality control (QC)

Next, we included only the participants that passed the following QC:

```{r quality_control}

MRIQcAll$NoIncidental <- ifelse((MRIQcAll$MRIF_SCORE== 3 | 
                                   MRIQcAll$MRIF_SCORE== 4 |
                                   MRIQcAll$MRIF_HYDROCEPHALUS == "yes"|         
                                   MRIQcAll$MRIF_HERNIATION == "yes"), 0, 1)
count(MRIQcAll,NoIncidental)

MRIQcAll %>% count(IQC_T1_OK_SER)

MRIQcAll %>% count(FSQC_QC)

MRIQcAll$T1FreeSurferQCOk <- ifelse((MRIQcAll$IQC_T1_OK_SER > 0 & 
                                       MRIQcAll$FSQC_QC == 1), 1, 0)

count(MRIQcAll,T1FreeSurferQCOk)

MRIQcAll %>% count(IQC_NBACK_OK_SER>0)

MRIQcAll %>% count(TFMRI_NBACK_BEH_PERFORMFLAG==1)

MRIQcAll %>% count(TFMRI_NBACK_ALL_BETA_DOF>200)

MRIQcAll$NbackBehDofOk <- ifelse((MRIQcAll$IQC_NBACK_OK_SER>0 &
                                    MRIQcAll$TFMRI_NBACK_BEH_PERFORMFLAG ==1 &
                                    MRIQcAll$TFMRI_NBACK_ALL_BETA_DOF>200), 1, 0)
count(MRIQcAll,NbackBehDofOk)

MRIQcAll$AllNbackQc <- ifelse((MRIQcAll$NoIncidental == 1 & 
                                 MRIQcAll$T1FreeSurferQCOk == 1 & 
                                 MRIQcAll$NbackBehDofOk == 1), 1, 0)
count(MRIQcAll,AllNbackQc)

Nback.QCed <- MRIQcAll %>% filter(AllNbackQc == 1)

```


## Remove Phillips

There was an issue was reported with the Philips scanners and it was recommended that the data from these scanners should be dropped. We did so:

```{r drop_phillips}
Nback.QCed %>% count(MRI_INFO_MANUFACTURER)

#remove phil and add beh during fMRI
Nback.QCedNoPhil <- Nback.QCed %>%
  filter(MRI_INFO_MANUFACTURER != 'Philips Medical Systems') 

#check how many variables in X2backVS0back and the list of ROIs
Nback.2backVS0back <- Nback.QCedNoPhil%>% select(.,starts_with("X2backvs0back"))
#colnames(Nback.2backVS0back)
```


Here are a list of responsevariable names which are used in the later analysis. Both short names ang long names are used in plotting.

```{r select_vars, data_pre1}

Resp_Var <- c('TFMRI_NB_ALL_BEH_C2B_RATE',
              "NIHTBX_PICVOCAB_UNCORRECTED", 
              "NIHTBX_FLANKER_UNCORRECTED",
              "NIHTBX_LIST_UNCORRECTED",
              "NIHTBX_CARDSORT_UNCORRECTED",
              "NIHTBX_PATTERN_UNCORRECTED",
              "NIHTBX_PICTURE_UNCORRECTED",
              "NIHTBX_READING_UNCORRECTED",
              "LMT_SCR_PERC_CORRECT",
              "PEA_RAVLT_LD_TRIAL_VII_TC",
              "PEA_WISCV_TRS")
resp_var_plotting_long <- c("2-back working memory",
  "Picture vocabulary test",
  "Flanker test",
  "List sorting working memory",
  "Dimentional change card sort test",
  "Pattern comparison processing speed test",
  "Picture sequence memory test",
  "Oral reading recognition test",
  "Little man task correct percentage",
  "RAVLT long delay trial VII total correct",
  "WISC_V matrix reasoning total raw score"
)
resp_var_plotting_short <- c("2-back Work Mem","Pic Vocab","Flanker","List Work Mem","Cog Flex","Pattern Speed","Seq Memory","Reading Recog","Little Man","Audi Verbal","Matrix Reason")
resp_var_plotting <- tibble("response" = all_of(Resp_Var), "longer_name"=resp_var_plotting_long,"short_name"=resp_var_plotting_short)

subj_info <- c('SUBJECTKEY', 'MRI_INFO_DEVICESERIALNUMBER', 'SITE_ID_L')

data_all_average <- Nback.QCedNoPhil %>%
  select(SUBJECTKEY, all_of(subj_info), all_of(Resp_Var),
         starts_with('X2backvs0back')) %>%
  rename_at(vars(-all_of(subj_info),-all_of(Resp_Var)),
            ~ str_replace(., 'X2backvs0back_ROI_', 'roi_'))
### checking whether the short names and ROI names in the data are the same
name_check <- which(short_names$roi != str_remove(names(select(data_all_average,starts_with("roi_"))),"roi_"))
print(name_check)

new_shorter_names <- short_names 
new_shorter_names$roiShort[97] <- "R Subcentral"
new_shorter_names$roiShort <-  str_squish(string = new_shorter_names$roiShort)
#new_shorter_names$roiShort <-  str_replace_all(string = new_shorter_names$roiShort, pattern = "\t", replacement = "")
### change ROI names to shorter ones (does not compat with formulas so not used)
#data_all_average <- data_all_average %>% rename_at(vars(starts_with("roi_")),~ new_shorter_names$roiShort)
```

## Selecting data

We also performed listwise deletion and dropped all participants for whom either the behavioral performance or the activation across some brain area was greater than 3 * IQR (interquartile range).

```{r data_pre2}

data_all_listwise <- data_all_average %>%
  drop_na() 

IQR_remove <- function(data_split){
  data_split%>%
  mutate_at(vars(- all_of(subj_info)), ~ ifelse(
    .x > quantile(.x, na.rm = TRUE)[4] + 3 * IQR(.x, na.rm = TRUE) |
    .x < quantile(.x, na.rm = TRUE)[2] - 3 * IQR(.x, na.rm = TRUE), 
    NA, .x)) %>%
  drop_na() %>%
  mutate_if(is.double, ~ (.x - mean(.x)) / sd(.x)) 
}
  

n_all <- nrow(data_all_average)
n_listwise <- nrow(data_all_listwise)
n_diff_all_listwise <- nrow(data_all_average) - nrow(data_all_listwise)

```

The outliers are removed with respect to training and testing data set. So no count of columns is displayed here.

## Check participant numbers across sites and scanners

Next we checked the number of participants across sites and scanners:
Note that site 22 and site08 have fewer than 100 participants whcn IQR rules were applied.

```{r check_scanners_sites}

nrow(data_all_listwise)

#26 scanners but 8 have fewer than 100 participants (as low as 3)
data_all_listwise  %>% count(MRI_INFO_DEVICESERIALNUMBER) %>% 
  summarize(`Number of scanners`=n()) %>%
  pander(split.cell = 80, split.table = Inf, justify = 'left')

data_all_listwise  %>% 
  count(MRI_INFO_DEVICESERIALNUMBER) %>%
  arrange(n) %>% 
  rename(`Scanner ID` = MRI_INFO_DEVICESERIALNUMBER, `Number of participants` = n) %>%
  pander(split.cell = 80, split.table = Inf, justify = 'left')

#19 sites, but 2 sites are fewer than 100 -> use sites?
data_all_listwise  %>% 
  count(SITE_ID_L) %>% 
  summarize(`Number of sites`=n())  %>%
  pander(split.cell = 80, split.table = Inf, justify = 'left')

data_all_listwise  %>% 
  count(SITE_ID_L) %>% 
  arrange(n) %>% 
  rename(`Site ID` = SITE_ID_L, `Number of participants` = n) %>%
  pander(split.cell = 80, split.table = Inf, justify = 'left')

# Remove site 22 and 8
data_all_listwise <- data_all_listwise %>%
  filter(SITE_ID_L != 'site22' & SITE_ID_L != 'site08')
```

## Check the distribution of all of the cognitive tasks
Most are normally distributed.

```{r plot_distribution_dvs}

#Look at distribution of NIHTBX_LIST_UNCORRECTED (i.e., working memory from Nback)
resp_names <-data_all_listwise %>% select(all_of(Resp_Var))%>%
  names()%>%
  set_names()

density_plot_grid <- resp_names %>%
  map(~ggplot(data_all_listwise,aes(x=.data[[.]])) 
      +stat_function(fun=dnorm, 
                color="skyblue", size = 1.5,
                args=list(mean=mean(data_all_listwise$.),
                          sd=sd(data_all_listwise$.))) +
  geom_density() +
  labs(x = NULL, y =NULL,title = resp_var_plotting$short_name[[which(resp_var_plotting$response==.)]])
)
title_density_plot <- ggdraw() + 
  draw_label(
    "Density plots of all the Cognitive Performance Variables",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )
plot_grid(title_density_plot,plot_grid(plotlist = density_plot_grid),nrow = 2 , rel_heights = c(0.1, 1))


```

```{r,echo=FALSE,eval=FALSE}
saveRDS(data_all_listwise, '/mnt/data/Yue script/task_data.RData')
```
# Modeling preparation

## Sample training and test data

To create the training and test data, we randomly sampled 75% of participants and assigned them to the training set. The rest of the participants were assigned to hold-out test data. 

```{r sample_train_test, eval=TRUE}
set.seed(123456)
data_vfold =vfold_cv(data = data_all_listwise, v=4,repeats = 1)
```


```{r, eval=FALSE,echo=FALSE}
saveRDS(data_vfold, file = "/mnt/data/Yue script/task_fold.RData")
```

Split the data for the cross validation grouped by site. Use one site as holdout and the other sites for training

```{r sample_hold_1_site }
unique_site <- length(unique(data_all_listwise$SITE_ID_L))

site_vfold <- group_vfold_cv(data = data_all_listwise, group = "SITE_ID_L", v= unique_site)
## the following two lines take the split results and transform it into a data frame
## so that all the results can be checked.
#model_data_1 <- site_vfold$splits[[1]]%>% analysis()
#holdout__data_1 <- site_vfold$splits[[1]] %>% assessment()
```
# Mass univariate modeling

## Fit simple regressions on training data & evaluate on test data

```{r fit_simple1, eval=TRUE}

## splits will be the `rsplit` object with the 90/10 partition
holdout_results <- function(.x,splits, ...) {
  # Fit the model to the 75%
  mod <- lm(..., data = analysis(splits)%>% IQR_remove())
  # Save the 25%
  holdout <- assessment(splits)%>% IQR_remove()
  # `augment` will save the predictions with the holdout data set
  res <- broom::augment(mod, newdata = holdout)
  preds <- predict(mod, newdata = holdout)
  performance <- cor(preds, holdout[[.x]])
  
  slope <- mod %>% broom::tidy() %>% 
    filter(term != '(Intercept)') %>%
    rename(roi = term)
  slope_corr <- slope %>% bind_cols(performance = performance)
  
  slope_corr
}

resp_result <- function(.x){
  x=.x
  formulas <- paste0(x ,' ~ ', colnames(select(data_all_listwise,-all_of(Resp_Var),-all_of(subj_info))))
  results_test_simple <-map(formulas, ~ holdout_results(.x=x,splits = data_vfold$splits[[1]],...)) %>% bind_rows() %>%
  mutate(FDR = p.adjust(p.value, method = 'fdr'),
          bonferroni= p.adjust(p.value, method = 'bonferroni'))
  return(results_test_simple)
}
```


```{r fit_simple_calculation, eval=FALSE}
simple_all_IQR <- map(.x=resp_names,~resp_result(.x))
```

```{r, eval=FALSE, echo=FALSE}
saveRDS(simple_all_IQR,file ="/mnt/data/Yue script/simple_reg_all_IQR.RData" )
```


```{r, echo=FALSE}
simple_all_IQR <- readRDS(file ="/mnt/data/Yue script/simple_reg_all.RData" )
```

## Out-of-sample, out-of-scanner predictive ablitiy for the mass univariate

```{r plotting_simple}

longer_all <-resp_names %>% map(.,~pivot_longer(simple_all_IQR[[.]],cols = c("bonferroni","FDR", "p.value"),names_to="p_val_type",values_to="p_vals"))
##To plot all the density of all the areas vurses significant areas after two corrections
##I set all the uncorrected p value to 0 to pass the screening in the plotting function
longer_all <-resp_names %>%map(.,~mutate(longer_all[[.]],plt_val = ifelse(p_val_type=="p.value",0,p_vals))) 
longer_all <-resp_names %>%map(.,~mutate(longer_all[[.]],plt_type = ifelse(p_val_type=="p.value","All",ifelse(p_val_type=="FDR","FDR","Bonferroni")))) 

sig_all <-  longer_all %>%map(.,~filter(.,plt_val < 0.05)%>%mutate(.,plt_type= as.factor(plt_type))%>%
                                mutate(.,plt_type = factor(.$plt_type,levels =c ("All","FDR","Bonferroni"))))
simple_plot_list <- resp_names %>%map(.,~ggplot(sig_all[[.]],aes(performance,color=plt_type, fill=plt_type)) +
  geom_histogram(binwidth = 0.01, position = 'identity',alpha=0.5) +
  scale_x_continuous(limits = c(-0.1, 0.25)) +
  scale_y_continuous(limits = c(0, 30)) +
  labs(x = NULL, fill = NULL, y = NULL,
       title = resp_var_plotting$short_name[[which(resp_var_plotting$response==.)]])+
    #scale_color_manual(values = c("darkgoldenrod1","brown2","cyan3"))+
     #scale_fill_manual(values = c("darkgoldenrod1","brown2","cyan3"))+
    guides(color=FALSE)
 )

title_simple_plot <- ggdraw() + 
  draw_label(
    "Out-of-sample Mass-Univariate Predictive Ability (Pearson's r)",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )
```

### Out-of-sample, out-of-scanner predictive ablitiy across corrections for mass univariate

```{r}
ggpubr::ggarrange(title_simple_plot,ggpubr::ggarrange(plotlist=simple_plot_list, common.legend = TRUE),nrow = 2 , heights = c(0.1, 1))  

 n_signif_fdr <- resp_names %>% map(.,~filter(simple_all_IQR[[.]],FDR < 0.05))  
 n_signif_fdr <- resp_names %>% map(.,~count(n_signif_fdr[[.]]))%>%do.call(rbind,.) 
 
 n_signif_bonf <- resp_names %>% map(.,~filter(simple_all_IQR[[.]], bonferroni< 0.05))  
 n_signif_bonf <- resp_names %>% map(.,~count(n_signif_bonf[[.]]))%>%do.call(rbind,.) 
 
 n_sig_all <- data.frame("var_name"=resp_var_plotting$short_name,"FDR_total"=n_signif_fdr$n,"BONF_total"=n_signif_bonf$n)%>% as_tibble()%>%print()

```

For the n-back behavioral performance, With FDR adjustment, there were `r as.numeric(n_signif_fdr[1,1])` significant ROIs out of the 167 total. With Bonferroni adjustment, there were `r as.numeric(n_signif_bonf[1,1])` significant ROIs.

## Statistical Inferences for the mass univeriate 
Plotting all significant areas for mass univariate with 2SE

```{r fit_simple2, fig.height=9, fig.width=8}
sig_all_wider_FDR <- resp_names %>% map(.,~filter(simple_all_IQR[[.]],FDR < 0.05))
sig_all_wider_FDR_rename <- resp_names %>% map(.,~mutate(sig_all_wider_FDR[[.]],roi = str_remove(roi, 'roi_')))
sig_all_wider_FDR_rename <- sig_all_wider_FDR_rename %>% map(.,~left_join( .,new_shorter_names,by="roi"))
roi_num_simple_FDR <- sig_all_wider_FDR_rename %>% map(.,~dim(.)[1])
max_roi_simple_FDR <- max(as.numeric(roi_num_simple_FDR))
sig_all_wider_FDR_rename <- resp_names %>% map(.,~mutate(sig_all_wider_FDR_rename[[.]],direction = ifelse(sig_all_wider_FDR_rename[[.]]$estimate >= median(sig_all_wider_FDR_rename[[.]]$estimate)|roi_num_simple_FDR[[.]] <= floor(max_roi_simple_FDR/2),"big","small")))

resp_names %>% map(~ggplot(sig_all_wider_FDR_rename[[.]],aes(x = fct_reorder(roiShort, estimate), y = estimate,
             ymin = estimate - 2 * std.error, ymax = estimate + 2 * std.error)) +
  geom_hline(yintercept = 0, linetype = 'dashed', col = 'grey60') +
  geom_pointrange(fatten = 1.5, col = 'grey60') +
  coord_flip() +
guides(colour = guide_legend(override.aes = list(size = 2.5)))+
  labs(x = 'Brain Regoins that passed FDR', y=NULL,
       title =paste0("Mass-Univariate Parameter Estimates (Training Set)\n",resp_var_plotting$longer_name[[which(resp_var_plotting$response==.)]]) ) +
  facet_wrap(~direction, scales = "free_y" ) +     
theme_bw() +  
#theme(axis.text.y = element_text(angle = 15)) +
theme(legend.title=element_blank()) +  
theme(legend.position = "top") + 
theme(
  axis.title.x = element_text(size = 20),
  axis.text.x = element_text(size = 10),
  axis.title.y = element_text(size = 10),
  axis.text.y = element_text(size = 10),
  legend.text = element_text(size = 10)) +
 theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
                     )
)
## print the summary statistics for rois passed FDR correction
## maximum
 max_FDR <-resp_names %>% map(., ~sig_all_wider_FDR_rename[[.]][which(sig_all_wider_FDR_rename[[.]]$performance==max(sig_all_wider_FDR_rename[[.]]$performance)),]%>% select(.,-roi,-direction)) %>% do.call(rbind,.)%>%select("estimate", "performance","FDR","bonferroni","roiShort")%>%print()
##minimum
min_FDR <-resp_names %>% map(., ~sig_all_wider_FDR_rename[[.]][which(sig_all_wider_FDR_rename[[.]]$performance==min(sig_all_wider_FDR_rename[[.]]$performance)),]%>% select(.,-roi,-direction)) %>% do.call(rbind,.)%>%select("estimate", "performance","FDR","bonferroni","roiShort")%>%print()
##median
median_FDR <-resp_names %>% map(., ~sig_all_wider_FDR_rename[[.]][which(sig_all_wider_FDR_rename[[.]]$performance==median(sig_all_wider_FDR_rename[[.]]$performance)),]%>% select(.,-roi,-direction)) %>% do.call(rbind,.)%>%select("estimate", "performance","FDR","bonferroni","roiShort")%>%print()
## print the mean parameter estimation and performance that passed FDR corredtion
FDR_mean_est <- resp_names %>% map(.,~mean(sig_all_wider_FDR_rename[[.]]$estimate))%>%do.call(rbind,.)
FDR_mean_perform <- resp_names %>% map(.,~mean(sig_all_wider_FDR_rename[[.]]$performance))%>%do.call(rbind,.)
FDR_sd_est <- resp_names %>% map(.,~sd(sig_all_wider_FDR_rename[[.]]$estimate))%>%do.call(rbind,.)
FDR_sd_perform <- resp_names %>% map(.,~sd(sig_all_wider_FDR_rename[[.]]$performance))%>%do.call(rbind,.)
FDR_print <- data.frame("var_name_FDR"=resp_var_plotting$short_name,"Mean_estimation"=FDR_mean_est,"SD_Estimation"=FDR_sd_est,"Mean_Performance"=FDR_mean_perform,"SD_performance"=FDR_sd_perform)%>% as_tibble()%>%print()

sig_all_wider_bonf <- resp_names %>% map(.,~filter(simple_all_IQR[[.]],bonferroni < 0.05))
sig_all_wider_bonf_rename <- resp_names %>% map(.,~mutate(sig_all_wider_bonf[[.]],roi = str_remove(roi, 'roi_')))
sig_all_wider_bonf_rename <- sig_all_wider_bonf_rename %>% map(.,~left_join( .,new_shorter_names,by="roi"))
roi_num_simple_bonf <- sig_all_wider_bonf_rename %>% map(.,~dim(.)[1])
max_roi_simple_bonf <- max(as.numeric(roi_num_simple_bonf))
sig_all_wider_bonf_rename <- resp_names %>% map(.,~mutate(sig_all_wider_bonf_rename[[.]],direction = ifelse(sig_all_wider_bonf_rename[[.]]$estimate >= median(sig_all_wider_bonf_rename[[.]]$estimate)|roi_num_simple_bonf[[.]] <= floor(max_roi_simple_bonf/2),"big","small")))
 
resp_names %>% map(~ggplot(sig_all_wider_bonf_rename[[.]],aes(x = fct_reorder(roiShort, estimate), y = estimate,
             ymin = estimate - 2 * std.error, ymax = estimate + 2 * std.error)) +
  geom_hline(yintercept = 0, linetype = 'dashed', col = 'grey60') +
  geom_pointrange(fatten = 1.5, col = 'grey60') +
  coord_flip() +
guides(colour = guide_legend(override.aes = list(size = 2.5)))+
  labs(x = 'Brain Regions that passed Bonferroni', y=NULL,
       title = paste0("Mass-Univariate Parameter Estimates (Training Set)\n",resp_var_plotting$longer_name[[which(resp_var_plotting$response==.)]]) ) +
  facet_wrap(~direction, scales = "free_y" ) +     
theme_bw() +  
#theme(axis.text.y = element_text(angle = 15)) +
theme(legend.title=element_blank()) +  
theme(legend.position = "top") + 
theme(
  axis.title.x = element_text(size = 20),
  axis.text.x = element_text(size = 10),
  axis.title.y = element_text(size = 10),
  axis.text.y = element_text(size = 10),
  legend.text = element_text(size = 10)) +
 theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
                     )
)
```

## Summary statistics for out-of-sample predicitve ability for the Mass Univariate
print the summary statistics for rois passed Bonf correction:   
  
### Maximum  
```{r}
 max_bonf <-resp_names %>% map(., ~sig_all_wider_bonf_rename[[.]][which(sig_all_wider_bonf_rename[[.]]$performance==max(sig_all_wider_bonf_rename[[.]]$performance)),]%>% select(.,-roi,-direction)) %>% do.call(rbind,.)%>%select("estimate", "performance","FDR","bonferroni","roiShort")%>%print()
```
  
### Minimum  
```{r}
min_bonf <-resp_names %>% map(., ~sig_all_wider_bonf_rename[[.]][which(sig_all_wider_bonf_rename[[.]]$performance==min(sig_all_wider_bonf_rename[[.]]$performance)),]%>% select(.,-roi,-direction)) %>% do.call(rbind,.)%>%select("estimate", "performance","FDR","bonferroni","roiShort")%>%print()
```
  
### Median  
```{r}
median_bonf <-resp_names %>% map(., ~sig_all_wider_bonf_rename[[.]][which(sig_all_wider_bonf_rename[[.]]$performance==median(sig_all_wider_bonf_rename[[.]]$performance)),]%>% select(.,-roi,-direction)) %>% do.call(rbind,.)%>%select("estimate", "performance","FDR","bonferroni","roiShort")%>%print()
```

### Mean parameter estimation and performance that passed Bonferroni

```{r}
bonf_mean_est <- resp_names %>% map(.,~mean(sig_all_wider_bonf_rename[[.]]$estimate))%>%do.call(rbind,.)
bonf_mean_perform <- resp_names %>% map(.,~mean(sig_all_wider_bonf_rename[[.]]$performance))%>%do.call(rbind,.)
bonf_sd_est <- resp_names %>% map(.,~sd(sig_all_wider_bonf_rename[[.]]$estimate))%>%do.call(rbind,.)
bonf_sd_perform <- resp_names %>% map(.,~sd(sig_all_wider_bonf_rename[[.]]$performance))%>%do.call(rbind,.)
bonf_print <- data.frame("var_name_bonf"=resp_var_plotting$short_name,"Mean_estimation"=bonf_mean_est,"SD_Estimation"=bonf_sd_est,"Mean_Performance"=bonf_mean_perform,"SD_performance"=bonf_sd_perform)%>% as_tibble()%>%print()

```

## Training coefficients vs. predictive ablitiy for the mass univariate

```{r fit_simple3, fig.width=6, fig.height=6}
slope_plot_grid <-resp_names %>% map(.,~ggplot(simple_all_IQR[[.]],aes(estimate, performance)) +
  geom_point(col = 'grey60') +
  labs(x = NULL, y = NULL,
         title =resp_var_plotting$short_name[[which(resp_var_plotting$response==.)]] )
                     )

title_slope_plot <- ggdraw() + 
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )
slope_plot_figure<- plot_grid(title_slope_plot,plot_grid(plotlist = slope_plot_grid, nrow=4, ncol=3),nrow = 2 , rel_heights = c(0.1, 1))

ggpubr::annotate_figure(slope_plot_figure,left= ggpubr::text_grob("Mass-Univariate Predictive Ability (Pearson's r)",size=15,rot=90),
                        bottom = ggpubr::text_grob("Mass-Univariate Training Coefficients",size=15))
```

## Cross-validate mass univaraite across sites
Set up folds & summary functions for cross-validation across sites

```{r simple_reg6 }
all_sample <- site_vfold$id

all_site <-  all_sample %>% map (.,~unique(assessment(site_vfold$splits[[which(site_vfold$id==.)]])$SITE_ID_L)) %>% do.call(rbind,.)
all_site <- as.vector(all_site)
all_site_number <- str_remove_all(all_site,"site")

site_result <- function(site_var,resp_var){
  data_split <- site_vfold$splits[[which(site_vfold$id==site_var)]]
  formula_site <- paste0(resp_var ,' ~ ', colnames(select(data_all_listwise,-all_of(Resp_Var),-all_of(subj_info))))
  results_test_simple <-map(formula_site,~holdout_results(.x=resp_var,splits = data_split,...)) %>% bind_rows()%>%
    mutate(site=unique(assessment(data_split)$SITE_ID_L))
  return(results_test_simple)
}

```

```{r fit_simple_cross_site, eval=FALSE}
leave_one_all_IQR <- vector("list", length = length(resp_names))
names(leave_one_all_IQR)<- resp_names
#this command runs 10*17*167 simple regressions
#pretty time-consuming. So not recommended to run
for(i in 1:length(resp_names)){
  leave_one_all_IQR[[resp_names[i]]]<- all_sample %>% map(.,~site_result(.,resp_var=resp_names[i]))%>%bind_rows() %>%
  mutate(FDR = p.adjust(p.value, method = 'fdr'),
          bonferroni= p.adjust(p.value, method = 'bonferroni'))
}
```

```{r, eval=FALSE,echo=FALSE}
saveRDS(leave_one_all_IQR, file = "/mnt/data/Yue script/simple_leave_one_site_all_IQR.RData")
```

```{r,echo=FALSE}
simple_leave_one_all_IQR <- readRDS(file = "/mnt/data/Yue script/simple_leave_one_site_all_IQR.RData")
```

## Leave one site out cross validation results.

```{r plotting_leave_one_site_simple}
simple_leave_one_all_IQR <- resp_names %>% map(., ~mutate(simple_leave_one_all_IQR[[.]],site=str_remove(simple_leave_one_all_IQR[[.]]$site,"site")))

simple_site_plot_grid <- resp_names %>% map(.,~ggplot(simple_leave_one_all_IQR[[.]],aes(x = site, y = performance)) +
  geom_jitter(width = 0.1, height = 0, size = 0.5, col = 'grey40') +
  geom_boxplot(alpha = 0.5, fill = 'grey80', col = 'grey40', outlier.colour = NA) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  labs(x = NULL, y = NULL,
       title =resp_var_plotting$short_name[[which(resp_var_plotting$response==.)]] )
)
title_simple_site <- ggdraw() + 
  draw_label(
   "Leave-One-Site-Out Mass-Univariate Predictive Ability",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )

simple_site_plot_figure<- plot_grid(title_simple_site,plot_grid(plotlist = simple_site_plot_grid),nrow = 2 , rel_heights = c(0.1, 1))

ggpubr::annotate_figure(simple_site_plot_figure,left= ggpubr::text_grob("Predictive Ability (Pearson's r)",size=15,rot=90),
                        bottom = ggpubr::text_grob("Sites",size=15))

## select the important areas for cross method plot
simple_leave_one_all_FDR_IQR <- simple_leave_one_all_IQR %>% map(.,~filter(.,FDR<=0.05)%>% group_by(.,site)%>%nest(.,data=-site))
simple_leave_one_all_bonf_IQR <- simple_leave_one_all_IQR %>% map(.,~filter(.,bonferroni<=0.05)%>% group_by(.,site)%>%nest(.,data=-site))
cross_site_median = function(resp_var,data_input,method){
    median_extract <- all_site_number %>% map(.,~median(data_input[[resp_var]]$data[[which(data_input[[resp_var]]$site==.)]]$performance))
  combined_results <- tibble(performance = as.numeric(median_extract),site=simple_leave_one_all_FDR_IQR$TFMRI_NB_ALL_BEH_C2B_RATE$site,
                              method=method,response=resp_var)
  combined_results$site <- paste0("site", combined_results$site)
  return(combined_results)
}

simple_leave_one_all_FDR_median_IQR<- resp_names %>% map (.,~cross_site_median(.,data_input=simple_leave_one_all_FDR_IQR,method = "FDR"))%>% bind_rows()%>%
                                        left_join(.,resp_var_plotting,by="response")
simple_leave_one_all_bonf_median_IQR<- resp_names %>% map (.,~cross_site_median(.,data_input=simple_leave_one_all_bonf_IQR,method = "Bonferroni"))%>% bind_rows()%>%left_join(.,resp_var_plotting,by="response")

```

## Leave-one-site-out predictive ablity for each roi for FDR and bonferroni

```{r fit_simple5, fig.height=9, fig.width=8}
rois_fdr <- simple_all_IQR %>%map(.,~filter(., FDR < 0.05) ) 
rois_fdr <- rois_fdr %>% map(.,~pluck(.,'roi')) 

rois_bonf <- simple_all_IQR %>%map(.,~filter(., bonferroni < 0.05) ) 
rois_bonf <- rois_bonf %>% map(.,~pluck(.,'roi')) 
nest_all <-  resp_names %>%map(., ~group_by(simple_leave_one_all_IQR[[.]],roi)) 
nest_all <-  resp_names %>%map(., ~nest(simple_leave_one_all_IQR[[.]],data=-roi))
roi_names <- nest_all[[resp_names[1]]]$roi
nest_all_list <- nest_all %>% map(., ~as.list(.))
nest_all_list <- nest_all_list%>% map (., ~.[["data"]])
for(i in 1:length(resp_names)){
  names(nest_all_list[[resp_names[i]]]) <- roi_names
}
nest_list_fdr <- resp_names %>% map(., ~nest_all_list[[.]][rois_fdr[[.]]]) 
nest_list_fdr <- resp_names %>% map(.,~bind_rows(nest_list_fdr[[.]],.id = "roi"))
nest_list_fdr <- nest_list_fdr %>% map(.,~mutate(., roi=str_remove(roi, "roi_"))%>%
                                         left_join( .,new_shorter_names,by="roi"))
roi_num_nest_list <- resp_names %>% map(.,~length(unique(nest_list_fdr[[.]]$roi)))
max_roi_nest_FDR <- max(as.numeric(roi_num_nest_list))
nest_list_fdr <- resp_names %>% map(.,~mutate(nest_list_fdr[[.]],direction = ifelse(nest_list_fdr[[.]]$estimate >= median(nest_list_fdr[[.]]$estimate)|roi_num_nest_list[[.]] <= floor(max_roi_nest_FDR/2),"big","small")))

resp_names %>% map(.,~ggplot(nest_list_fdr[[.]],aes(x = roiShort, y = performance)) +
  geom_jitter(width = 0.1, height = 0, size = 0.5) +
  geom_boxplot(alpha = 0.5, fill = 'grey80', col = 'grey40', outlier.colour = NA) +
  labs(x = "Regions significant after FDR correction", y = "Predictive Ability across sites (Pearson's r)",
       title =paste0("Out-Of-Site Mass-Univariate Predictive Ability\n" , resp_var_plotting$longer_name[[which(resp_var_plotting$response==.)]] )) +
  coord_flip()+  
    facet_wrap(~direction, scales = "free_y" ) +
    guides(colour = guide_legend(override.aes = list(size = 2.5)))+theme(
    strip.background = element_blank(),
    strip.text.x = element_blank())+ 
   theme(axis.title.y = element_text(size = 16),
         axis.title.x = element_text(size = 16),
         plot.title = element_text(size=16))
) 

nest_list_bonf <- resp_names %>% map(., ~nest_all_list[[.]][rois_bonf[[.]]]) 
nest_list_bonf <- resp_names %>% map(.,~bind_rows(nest_list_bonf[[.]],.id = "roi"))
nest_list_bonf <- nest_list_bonf %>% map(.,~mutate(., roi=str_remove(roi, "roi_"))%>%
                                         left_join( .,new_shorter_names,by="roi"))
roi_num_nest_list_bonf <- resp_names %>% map(.,~length(unique(nest_list_bonf[[.]]$roi)))
max_roi_nest_bonf <- max(as.numeric(roi_num_nest_list_bonf))
nest_list_bonf <- resp_names %>% map(.,~mutate(nest_list_bonf[[.]],direction = ifelse(nest_list_bonf[[.]]$estimate >= median(nest_list_bonf[[.]]$estimate)|roi_num_nest_list_bonf[[.]] <= floor(max_roi_nest_bonf/2),"big","small")))
resp_names %>% map(.,~ggplot(nest_list_bonf[[.]],aes(x = roiShort, y = performance)) +
  geom_jitter(width = 0.1, height = 0, size = 0.5) +
  geom_boxplot(alpha = 0.5, fill = 'grey80', col = 'grey40', outlier.colour = NA) +
  labs(x = "ROI significant after Bonferroni correction", y = "Predictive Ability across sites (Pearson's r)",
       title = paste0("Out-Of-Site Mass-Univariate Predictive Ability\n" , resp_var_plotting$longer_name[[which(resp_var_plotting$response==.)]] )) +
  coord_flip()+  
    facet_wrap(~direction, scales = "free_y" ) +
    guides(colour = guide_legend(override.aes = list(size = 2.5)))+theme(
    strip.background = element_blank(),
    strip.text.x = element_blank())+ 
   theme(axis.title.y = element_text(size = 16),
         axis.title.x = element_text(size = 16),
         plot.title = element_text(size=16))
) 

```

# OLS regression

## OLS out-of-sample predictive ability across tasks

```{r fit_ols1}
ols_var_all_train_IQR <- resp_names %>% map(.,~select(analysis(data_vfold$splits[[1]])%>% IQR_remove(),.,starts_with("roi")))
ols_var_all_test_IQR <- resp_names %>% map(.,~select(assessment(data_vfold$splits[[1]])%>% IQR_remove(),.,starts_with("roi")))
fit_ols_all <- map(.x = resp_names, ~lm(paste0(.x, "~ ."), data = ols_var_all_train_IQR[[.x]]))

rsq_fit <- fit_ols_all %>%  map(.,~summary(.)$adj.r.squared)%>% do.call(rbind,.)
 tibble(response=names(fit_ols_all),rsquared = rsq_fit[,1])%>% left_join(.,resp_var_plotting ,by="response")%>% 
  select("longer_name","rsquared")%>%
  pander(split.cell = 80, split.table = Inf, justify = 'left')

preds_ols_all <- resp_names %>% map(.,~predict(fit_ols_all[[.]], newdata = ols_var_all_test_IQR[[.x]])) 

predvsreal_ols_all  <- resp_names %>% map(., ~ tibble(predicted = preds_ols_all[[.]], observed=select(assessment(data_vfold$splits[[1]])%>% IQR_remove(),.))) 

cor_ols_all <- resp_names %>% map(.,~cor(preds_ols_all[[.]], ols_var_all_test_IQR[[.]][[.]])) 
rmse_ols_all <- resp_names %>% map(.,~sqrt(mean((preds_ols_all[[.]] - ols_var_all_test_IQR[[.]][[.]]) ^ 2))) 

ols_pred_all <- resp_names %>% map(., ~ggplot(predvsreal_ols_all[[.]], aes(x = scale(predicted) , y = scale(observed[[.]]))) +
  geom_jitter(height = 0.1, width = 0.1, size = 1, col = 'grey60') +
  geom_smooth(method = 'lm', se = FALSE, col = 'black')  +
  labs(x = NULL,
       y = NULL,
       title = paste (resp_var_plotting$short_name[[which(resp_var_plotting$response==.)]],'\nr = ',round(cor_ols_all[[.]], 3))) 
                     )
  title_ols_pred_plot <- ggdraw() + 
  draw_label(
    "Out-of-Sample OLS Predictive Ability",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )
  ols_pred_all_figure<- plot_grid(title_ols_pred_plot,plot_grid(plotlist = ols_pred_all),nrow = 2 , rel_heights = c(0.1, 1))

  ggpubr::annotate_figure(ols_pred_all_figure,left= ggpubr::text_grob("Observed Cognitive Performance (Z)",size=15,rot=90),
                        bottom = ggpubr::text_grob("Predicted Cognitive Performance (Z)",size=15))
```
  
## OLS out-of-sample predictive ability for the n-back only

```{r,fig.width=8,fig.height=6}  

ggplot(predvsreal_ols_all[[resp_names[1]]], aes(x = scale(predicted) , y = scale(observed) )) +
  geom_jitter(height = 0.1, width = 0.1, size = 1, col = 'grey60') +
  geom_smooth(method = 'lm', se = FALSE, col = 'black') +
  labs(x =paste0("Predicted ",  resp_var_plotting$short_name[[which(resp_var_plotting$response==resp_names[1])]] ," (Z)")  ,
       y = paste0("Observed\n",  resp_var_plotting$short_name[[which(resp_var_plotting$response==resp_names[1])]] ," (Z)"),
       title = paste ("Out-of-Sample OLS\nPredictive Ability ",'r = ',round(cor_ols_all[[resp_names[1]]], 2)))+
       theme(axis.text=element_text(size=28),
        axis.title=element_text(size=28),
        plot.title = element_text(size=32))
```

## OLS statistical Inference

```{r fit_ols2}
tidy_fit_ols_all <-fit_ols_all %>%  map(., ~broom::tidy(.))
tidy_fit_ols_all <- tidy_fit_ols_all %>%   map(.,~filter(.,term != '(Intercept)' & p.value < 0.05 )%>%
                                             mutate(.,roi = str_remove(term, 'roi_'))%>%
                                         left_join( .,new_shorter_names,by="roi")%>%
                                         mutate(.,direction = ifelse(estimate >= median(estimate), "big","small")))

resp_names %>% map(~ggplot(tidy_fit_ols_all[[.]],aes(fct_reorder(roiShort, estimate), estimate, 
             ymin = estimate - 2 * std.error, 
             ymax = estimate + 2 * std.error)) +
  geom_hline(yintercept = 0, linetype = 'dashed', col = 'grey60') +
  geom_pointrange(fatten = 1.5, col = 'grey60') +
  coord_flip() +
  labs(x = 'Explanatory variables (Brain Regions)', y = 'Coefficients (± 2 std. errors)',
       title = paste0(resp_var_plotting$longer_name[[which(resp_var_plotting$response==.)]],
       '\nOLS Coeffcients (p < .05)')) + 
     facet_wrap(~ direction, scales = 'free_y') +
                     theme(
                       axis.title.x = element_text(size = 15),
                       axis.text.x = element_text(size = 12),
                       axis.title.y = element_text(size = 15),
                       axis.text.y = element_text(size = 12),
                       legend.text = element_text(size = 10),
                       plot.title = element_text(size=16)) + 
     theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
))


n_sig_ols <- tidy_fit_ols_all %>% map(.,~filter(., p.value< 0.05) ) 
n_sig_ols %>%map(.,~count(.))%>%do.call(rbind,.)%>% print()
```

## cross site functions for OLS

```{r fit_ols3, warning=FALSE}
ols_site <- function(resp_var,data_split = data_vfold$splits[[1]]){
     #recipe train and test data are from ols as the variables are the same
  data_train <- analysis(data_split)%>%IQR_remove()
  data_test <- assessment(data_split)%>%IQR_remove()
  ols_data_train <- select(data_train, resp_var, starts_with("roi"))
  ols_data_test <- select(data_test,resp_var,starts_with("roi"))
norm_recipe <- recipe(as.formula(paste0(resp_var, "~ .")) , data = ols_data_train) %>%
  step_dummy(all_nominal()) %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors())  %>% 
  # estimate the means and standard deviations
  prep(training = ols_data_train, retain = TRUE)
## model
ols_mod <- linear_reg(penalty = tune() ,mixture =tune()) %>% 
  set_engine("lm") 
fit_ols <- ols_mod %>% fit(as.formula(paste0(resp_var, "~ .")),data= ols_data_train)
pred_fit <-predict.model_fit(fit_ols,new_data = ols_data_test)
corval <- cor(pred_fit$.pred, ols_data_test[[resp_var]])

site_output <- tibble(performance = corval, site =unique(data_test$SITE_ID_L))

site_output
}

ols_site_all <- function(resp_var){
site_ols_all <- all_sample %>% future_map(.,~ols_site(all_of(resp_var), data_split=site_vfold$splits[[which(site_vfold$id==.)]]))
site_ols_all<- bind_rows(site_ols_all)
site_ols_all <- site_ols_all %>% mutate(response=resp_var,method="OLS")
return(site_ols_all)
}


ols_cross_site <- vector("list", length = length(resp_names))
names(ols_cross_site)<- resp_names
 for(i in 1:length(resp_names)){
   ols_cross_site[[i]] <- ols_site_all(resp_names[i])
 }

ols_cross_site_list <- ols_cross_site

ols_cross_site <-  bind_rows(ols_cross_site)
ols_cross_site <- left_join (ols_cross_site,resp_var_plotting, by="response")
ols_site <- ols_cross_site %>%
ggplot(aes(x = reorder(short_name,performance), y = performance)) +
  geom_jitter(width = 0.1, height = 0, size = 0.5) +
  geom_boxplot(alpha = 0.5, fill = 'grey80', col = 'grey40', outlier.colour = NA) +
  labs(x=NULL,y=NULL,title="OLS") +
  coord_flip()

ols_site
```

# Elastic net  
Elastic net is based on tidymodels. Once tuned eNetXplorer is used for stats inference

```{r tidy_models1_enet, eval=TRUE}

enet_tuning <- function(resp_var,data_split = data_vfold$splits[[1]]){
     #recipe train and test data are from ols as the variables are the same
  data_train <- analysis(data_split)%>% IQR_remove()
  data_test <- assessment(data_split)%>% IQR_remove()
  ols_data_train <- select(data_train, resp_var, starts_with("roi"))
  ols_data_test <- select(data_test,resp_var,starts_with("roi"))
norm_recipe <- recipe(as.formula(paste0(resp_var, "~ .")) , data = ols_data_train) %>%
  step_dummy(all_nominal()) %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors())  %>% 
  # estimate the means and standard deviations
  prep(training = ols_data_train, retain = TRUE)
## model
glmn_mod <- linear_reg(penalty = tune() ,mixture =tune()) %>% 
  set_engine("glmnet") 
set.seed(123456)
all_rs <- rsample::vfold_cv(data=ols_data_train,v = 10,repeats = 1)#10fold split within the original 75% training data
glmn_wfl <- workflow()%>%
  add_recipe(norm_recipe)%>%
  add_model(glmn_mod)
##penalty is lambda, mixture is alpha
##log transformed to get lambda between 0.025 to 10
glmn_set <- dials::parameters(penalty(range = c(-5,1), trans = log10_trans()),mixture())
## 100 levels of lambda and 10 levels of alpha
glmn_grid <- grid_regular(glmn_set, levels = c(400,100))
ctrl <- control_grid(save_pred = TRUE, verbose = TRUE)

glmn_tune <- tune_grid(glmn_wfl,
            resamples = all_rs,
            grid = glmn_grid,
            metrics = metric_set(rsq_trad),##use traditional r square because there is no correlation
            control = ctrl)
##select the best tuned lambda and alpha
best_glmn <- select_best(glmn_tune, metric = "rsq_trad")
## use the best tunes parameters to fit the test data
glmn_wfl_final <- 
  glmn_wfl %>%
  finalize_workflow(best_glmn) %>%
  fit(data = ols_data_train)
pred_glmn <- predict(glmn_wfl_final, new_data =ols_data_test)
##compute the correlation between predicted results and the test data 
performance_glmn <- cor(pred_glmn$.pred,ols_data_test[[resp_var]])
best_glmn <- best_glmn %>% mutate(performance=performance_glmn)
return(best_glmn)
}
```

```{r fit_enet_tuning, eval=FALSE}
#this line tuning all the parameters in all 11 response variables
# time consuming so the default of this section is set to eval= FALSE
glmn_tune_all_IQR <- resp_names%>% future_map(.,~enet_tuning(.))
```

```{r,eval=FALSE,echo=FALSE}
saveRDS(glmn_tune_all_IQR,file ="/mnt/data/Yue script/glmn_tune_all_IQR.RData" )
```

```{r get_tuned_parameters,echo=FALSE}
glmn_tuning_all_IQR <- readRDS(file ="/mnt/data/Yue script/glmn_tune_all_IQR.RData")
```


```{r fit_enet_data}
enet_test <- select(assessment(data_vfold$splits[[1]])%>%IQR_remove() ,starts_with("roi"))
enet_train <- select(analysis(data_vfold$splits[[1]])%>%IQR_remove(),starts_with("roi"))
enet_resp_train <- resp_names %>% map(., ~select(analysis(data_vfold$splits[[1]])%>%IQR_remove(),starts_with(.)))
enet_resp_test <- resp_names %>% map(., ~select(assessment(data_vfold$splits[[1]])%>%IQR_remove(),starts_with(.)))
```

```{r fit_enet1, eval=FALSE}
### NOT RUN by default, takes long time

fit_enet_all_IQR <-resp_names %>% future_map(.,~eNetXplorer(x = as.matrix(enet_train) , y = as.vector(enet_resp_train[[.]][[.]]), alpha = glmn_tuning_all_IQR[[.]]$mixture, n_fold = 10,nlambda.ext = 1000, nlambda = 1000, scaled = TRUE, seed = 123456)) 
```

```{r,eval=FALSE,echo=FALSE}
saveRDS(fit_enet_all_IQR, '/mnt/data/Yue script/fit_ridge_all_IQR.RData')
```

```{r,echo=FALSE}
fit_enet_all_IQR  <- read_rds('/mnt/data/Yue script/fit_ridge_all_IQR.RData')
```

## Hyperparameter tuning for elastic net

```{r fit_enet2}
lambdas_all <- vector("list", length = length(resp_names))
names(lambdas_all)<- resp_names
lambdas_all_best <- vector("list", length = length(resp_names))
names(lambdas_all_best)<- resp_names
summary_enet_all <- vector("list", length = length(resp_names))
names(summary_enet_all)<- resp_names

for(i in 1:length(resp_names)){
  lambdas_all[[resp_names[i]]] <- fit_enet_all_IQR[[resp_names[i]]][["lambda_values"]]
lambdas_all_best[[resp_names[i]]] <- fit_enet_all_IQR[[resp_names[i]]][["best_lambda"]]
summary_enet_all[[resp_names[i]]]<- as_tibble(summary(fit_enet_all_IQR[[resp_names[i]]])[[2]]) %>% slice(1)
}

summary_enet_all %>% bind_rows() %>% 
  mutate(respones = resp_var_plotting$short_name)%>%
  rename(.,Alpha = alpha, `Best-tune lambda` = lambda.max, 
         `Accuracy (Pearson r)` = QF.est, 
         `P-value` = model.vs.null.pval) %>%
  pander(split.cell = 80, split.table = Inf, justify = 'left')

alpha_vals <- glmn_tuning_all_IQR %>% map(.,~paste0("a",.[["mixture"]])) 

enet_lambda_grid <-resp_names%>% map(.,~qplot(fit_enet_all_IQR[[.]][["lambda_values"]][[alpha_vals[[.]]]], fit_enet_all_IQR[[.]][["lambda_QF_est"]][[alpha_vals[[.]]]], geom = 'line') + 
#  scale_y_continuous(breaks = seq(0, 0.6, by = 0.1)) +
  scale_x_log10() +
  geom_vline(xintercept = lambdas_all_best[[.]], col = 'red', linetype = 'dashed') +
  labs(x = NULL, y = NULL, title =resp_var_plotting$short_name[[which(resp_var_plotting$response==.)]] )
  #+theme(axis.title.y=element_blank(),
   #     axis.text.y=element_blank(),
    #    axis.ticks.y=element_blank())
  )  
title_enet_lambda <- ggdraw() + 
  draw_label(
    "Elastic Net Lambda (Penalty) Parameter Tuning",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0.1, 0.1, 0.1, 7)
  )

enet_lambda_all_figure<- plot_grid(title_enet_lambda,plot_grid(plotlist = enet_lambda_grid,nrow=4,ncol=3),nrow = 2 , rel_heights = c(0.1, 1))

ggpubr::annotate_figure(enet_lambda_all_figure,left= ggpubr::text_grob("Cross Validated Predictive Ability\n(Pearson's r)",size=15,rot=90),
                        bottom = ggpubr::text_grob("Lambda",size=15))
```

## Out-of-sample, out-of-scanner predictive ability of the elastic net 

```{r fit_enet3}

fit_enet_single_all <- resp_names %>% map(.,~glmnet(x = as.matrix(select(ols_var_all_train_IQR[[.]], starts_with("roi"))) , y = ols_var_all_train_IQR[[.]][[.]], alpha = glmn_tuning_all_IQR[[.]]$mixture, lambda = glmn_tuning_all_IQR[[.]]$penalty)) 
preds_enet_all <- resp_names%>% map(.,~predict(fit_enet_single_all[[.]] , newx = as.matrix(select(ols_var_all_test_IQR[[.]], starts_with("roi")))))

predvsreal_enet_all <- resp_names %>% map (.,~tibble(predicted = preds_enet_all[[.]], observed = as.numeric(ols_var_all_test_IQR[[.]][[.]]))) 

cor_enet_all <- resp_names %>% map(.,~cor(preds_enet_all[[.]], as.numeric(ols_var_all_test_IQR[[.]][[.]])))   
rmse_enet_all <-resp_names %>% map(.,~sqrt(mean((preds_enet_all[[.]] - as.numeric(ols_var_all_test_IQR[[.]][[.]])) ^ 2))) 

enet_single_plot <- resp_names %>% map(.,~ggplot(predvsreal_enet_all[[.]], aes(x = scale(predicted) , y = scale(observed) )) +
  geom_jitter(height = 0.1, width = 0.1, size = 1, col = 'grey60') +
  geom_smooth(method = 'lm', se = FALSE, col = 'black') +
  labs(x = NULL,
       y = NULL,
       title = paste (resp_var_plotting$short_name[[which(resp_var_plotting$response==.)]],'\nr = ',round(cor_enet_all[[.]], 3))))
  
title_enet_pred_plot <- ggdraw() + 
  draw_label(
    "Out-of-Sample Elastic Net Predictive Ability",
    fontface = 'bold',
    x = 0,
    hjust = 0
  ) +
  theme(
    # add margin on the left of the drawing canvas,
    # so title is aligned with left edge of first plot
    plot.margin = margin(0, 0, 0, 7)
  )



enet_pred_all_figure<- plot_grid(title_enet_pred_plot,plot_grid(plotlist = enet_single_plot),nrow = 2 , rel_heights = c(0.1, 1))

ggpubr::annotate_figure(enet_pred_all_figure,left= ggpubr::text_grob("Observed Cognitive Performance (Z)",size=15,rot=90),
                        bottom = ggpubr::text_grob("Predicted Cognitive Performance (Z)",size=15))
```

## Out-of-sample predictive ability of the elastic net on n back

```{r fit_enet4 ,fig.width=8,fig.height=6}
ggplot(predvsreal_enet_all[[resp_names[1]]], aes(x = scale(predicted) , y = scale(observed) )) +
  geom_jitter(height = 0.1, width = 0.1, size = 1, col = 'grey60') +
  geom_smooth(method = 'lm', se = FALSE, col = 'black') +
  labs(x =paste0("Predicted ",  resp_var_plotting$short_name[[which(resp_var_plotting$response==resp_names[1])]] ," (Z)")  ,
       y = paste0("Observed\n",  resp_var_plotting$short_name[[which(resp_var_plotting$response==resp_names[1])]] ," (Z)"),
       title = paste ("Out-of-Sample Elastic Net\nPredictive Ability ",'r = ',round(cor_enet_all[[resp_names[1]]], 2)))+
       theme(axis.text=element_text(size=28),
        axis.title=element_text(size=28),
        plot.title = element_text(size=32))

```

## Stats inference of elastic net via enetXplorer

```{r fit_enet5}

extract_tibble <- function(elastic_mod, alpha_index) {
   variable <- elastic_mod$feature_coef_wmean[, alpha_index] %>% names()
    wmean <- elastic_mod$feature_coef_wmean[, alpha_index]
    wsd <- elastic_mod$feature_coef_wsd[, alpha_index]
    null_wmean <- elastic_mod$null_feature_coef_wmean[, alpha_index]
    null_wsd <- elastic_mod$null_feature_coef_wsd[, alpha_index]
    pvalue <- elastic_mod$feature_coef_model_vs_null_pval[, alpha_index]
    
    tib <- tibble(variable, wmean, wsd, null_wmean, null_wsd, pvalue)
   
    tib <- tib %>%
      gather(key = 'placeholder', value = 'value', wmean, wsd, null_wmean, null_wsd) %>%
      mutate(type = ifelse(str_detect(placeholder, 'null'), 'null', 'target'),
             placeholder = (str_remove(placeholder, 'null_'))) %>%
      mutate(type = factor(type, labels = c('Null', 'Target'))) %>%
      spread(placeholder, value)
    tib
}


 elastic_mod <- fit_enet_all_IQR[[resp_names[1]]]
    alpha_index <- paste0("a",glmn_tuning_all_IQR[[resp_names[1]]]$mixture)

    
  coefs_enet_all <- resp_names %>%  map(.,~extract_tibble(fit_enet_all_IQR[[.]], alpha_index = paste0("a",glmn_tuning_all_IQR[[.]]$mixture)))
    coefs_enet_all <- coefs_enet_all  %>% map(.,~filter(.,pvalue < 0.05) %>%
  mutate(.,type = ifelse(type == 'Null', 'Null permuted models', 'Target models'),
         roi = str_remove(variable, 'roi_'))%>%left_join( .,new_shorter_names,by="roi"))
roi_num_enet <- coefs_enet_all %>% map(.,~dim(.)[1])
max_roi_enet <- max(as.numeric(roi_num_enet))

coefs_enet_test <- coefs_enet_all[[resp_names[1]]] %>% group_by(type)
coefs_enet_test <- coefs_enet_test%>% nest(-type)
 coefs_enet_test[[2]][[1]] <- coefs_enet_test[[2]][[1]] %>% mutate(direction1 = ifelse(coefs_enet_test[[2]][[1]]$wmean >= median(coefs_enet_test[[2]][[1]]$wmean)|roi_num_enet[[resp_names[1]]] <= floor(max_roi_enet/2),"big","small"))
coefs_enet_test[[2]][[2]] <- coefs_enet_test[[2]][[2]] %>% mutate(direction1=coefs_enet_test[[2]][[1]]$direction1)
coefs_enet_test <- coefs_enet_test %>% unnest()

coefs_enet_all <- coefs_enet_all%>%map(.,~group_by(.,type)) 
coefs_enet_all <- coefs_enet_all%>%map(.,~nest(.,-type)) 
for(i in 1:length(resp_names)){
  coefs_enet_all[[resp_names[i]]][["data"]][[2]]<-coefs_enet_all[[resp_names[i]]][["data"]][[2]] %>% mutate(direction = ifelse(coefs_enet_all[[resp_names[i]]][["data"]][[2]]$wmean >= median(coefs_enet_all[[resp_names[i]]][["data"]][[2]]$wmean)|roi_num_enet[[resp_names[i]]] <= floor(max_roi_enet/2),"big","small"))
  coefs_enet_all[[resp_names[i]]][["data"]][[1]] <- coefs_enet_all[[resp_names[i]]][["data"]][[1]] %>% mutate(direction=coefs_enet_all[[resp_names[i]]][["data"]][[2]]$direction)
}

coefs_enet_all <- coefs_enet_all %>%map(.,~unnest(.)) 

resp_names %>% map(.,~ggplot(coefs_enet_all[[.]], aes(x = fct_reorder(roiShort, wmean), 
             y = wmean, 
             ymax = wmean + 2 * wsd, ymin = wmean - 2 * wsd,
             col = type)) +
  geom_pointrange(fatten = 0.5, key_glyph = 'point') +
  scale_y_continuous(labels = numform::ff_num(zero = 0, digits = 2)) + 
  scale_color_grey(start = 0.7, end = 0.5) +
  coord_flip() +
  guides(colour = guide_legend(override.aes = list(size = 2.5)))+
  labs(x = 'Explanatory Variables (Brain Regions)', y = 'Averaged Coefficient Across Models (±2 Std. dev)', col = 'Model type',
       title = paste0(resp_var_plotting$longer_name[[which(resp_var_plotting$response==.)]],"\nElastic Net Coefficients (p < .05)")) +
  facet_wrap(~ direction, scales = 'free_y') +
  scale_color_manual(values = c("#56B4E9", "black"),labels = c("Permuted Null", "Target")) +     
  theme_bw() +  
#theme(axis.text.y = element_text(angle = 15)) +
theme(legend.title=element_blank()) +  
theme(legend.position = "top") + 
theme(
  axis.title.x = element_text(size = 15),
  axis.text.x = element_text(size = 12),
  axis.title.y = element_text(size = 15),
  axis.text.y = element_text(size = 12),
  legend.text = element_text(size = 15),
  plot.title = element_text(size=15)) +
 theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()
) 
+ theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
)

n_signif_enet_all <- coefs_enet_all %>% map(.,~filter(.,type == 'Target models')%>%count())%>% bind_rows()
n_sig_enet_all <- data.frame("var_name"=resp_var_plotting$short_name,"ENET_total"=n_signif_enet_all$n)%>% as_tibble()%>%print()
```

## Cross-validate enet regression across sites

```{r glmnet_tuning_all_site, eval= TRUE}
enet_site_all <- function(resp_var){
site_tuning_all <- all_sample %>% future_map(.,~enet_tuning(resp_var, data_split=site_vfold$splits[[which(site_vfold$id==.)]]))
names(site_tuning_all)<- all_sample %>% map (.,~unique(assessment(site_vfold$splits[[which(site_vfold$id==.)]])$SITE_ID_L)) 
site_tuning_all<- site_tuning_all %>% bind_rows()
site_tuning_all <- site_tuning_all %>% mutate(site=all_site, response=resp_var,method="Elastic Net")
return(site_tuning_all)
}

```

```{r glmnet_tuning_all_site_computing, eval= FALSE}
enet_site_tuning_all_IQR <- resp_names %>% future_map(.,~enet_site_all(resp_var=.))
```

```{r, eval=FALSE,echo=FALSE}
saveRDS(enet_site_tuning_all_IQR,file ="/mnt/data/Yue script/enet_site_tuning_all_IQR.RData" )
```

# Out-of-site predictive ablitiy across methods

```{r,echo=FALSE}
enet_site_tune_all_IQR <- readRDS(file ="/mnt/data/Yue script/enet_site_tuning_all_IQR.RData")
```

```{r fit_enet4}
enet_site_tune_all_plot <- enet_site_tune_all_IQR %>% bind_rows()
enet_site_tune_all_plot <- left_join(enet_site_tune_all_plot,resp_var_plotting,by="response")

joint_enet_tune_all <- enet_site_tune_all_plot %>% select(performance, site, method, longer_name, short_name, response)
all_method_performance <- bind_rows(joint_enet_tune_all,ols_cross_site,simple_leave_one_all_FDR_median_IQR,simple_leave_one_all_bonf_median_IQR)%>%
  mutate(method= as.factor(method))%>%
  mutate(method = factor(method,levels =c ("FDR","Bonferroni","OLS","Elastic Net")))


all_method_performance%>%
ggplot(aes(x = reorder(short_name,performance), y = performance, fill=method,color=method)) +
  geom_jitter(width = 0.1, height = 0, size = 0.5) +
  geom_boxplot(alpha = 0.5,  outlier.colour = NA, position = "identity") +
  labs(x = NULL, y=NULL,title="Out-of-site Predictive Ability (Pearson's r)") +
  coord_flip()+theme(axis.text=element_text(size=15),
        axis.title=element_text(size=15,face="bold"),
        legend.position = "bottom",
        legend.title=element_blank(),
        legend.text = element_text( size=15, face="bold"),
        plot.title = element_text(size=17))

```

```{r plotting_all_methods_against_simple}

simple_site_FDR  <- simple_leave_one_all_FDR_IQR%>%map(.,~unnest(.)%>% mutate(method="FDR")) 
simple_site_bonf <- simple_leave_one_all_bonf_IQR %>% map(.,~unnest(.)%>%mutate(method="Bonferroni"))
ols_site <- ols_cross_site_list %>% map(.,~dplyr::select(., method, site,performance)%>%mutate(site = str_remove_all(site,"site")))
enet_site <- enet_site_tune_all_IQR %>% map(.,~select(.,method,site,performance)%>%mutate(site = str_remove_all(site,"site")))
cross_site_multi <- resp_names %>% map(.,~bind_rows(ols_site[[.]],enet_site[[.]]))


resp_names %>%map(.,~ggplot(cross_site_multi[[.]], aes(site, performance, col = method)) +
  geom_point(key_glyph = "point", size = 3) +
  geom_jitter(data = simple_site_FDR[[.]], height = 0, width = 0.2, size = 0.5,
              key_glyph = "point") +
  geom_boxplot(data = simple_site_FDR[[.]], alpha = 0.75, outlier.colour = NA,
               key_glyph = "point")+
  geom_jitter(data = simple_site_bonf[[.]], height = 0, width = 0.2, size = 0.5,
              key_glyph = "point") +
  geom_boxplot(data = simple_site_bonf[[.]], alpha = 0.75, outlier.colour = NA,
               key_glyph = "point") +
 # scale_x_discrete(guide = guide_axis(n.dodge = )) +
  scale_color_manual(breaks=c("Elastic Net","OLS", "Bonferroni","FDR"),
    values = c( "#C77CFF","#00BFC4" ,"#7CAE00","#F8766D" )) +
  guides(colour = guide_legend(override.aes = list(size = 2.5)))+
  labs(x = 'Site', y=NULL, col = 'Model',
       title  = paste0("Out-of-site Predictive Ability (Pearson's r)\n",resp_var_plotting$longer_name[[which(resp_var_plotting$response==.)]]))+
  theme(axis.text.x=element_text(size=16, angle = 45),
        axis.text.y=element_text(size=16),
        axis.title.y=element_text(size=18),
        axis.title.x=element_text(size=18),
        plot.title=element_text(size=20),
        legend.position = "right",
        legend.title=element_blank(),
        legend.text = element_text( size=18)))   

```

# VIF
we used the training data and OLS to compute the VIF

```{r fit_ols4}
vifs_ols_all <- resp_names %>% future_map(.,~ols_vif_tol(fit_ols_all[[.]]))
vifs_ols_all <- vifs_ols_all %>% map(.,~mutate(., term=Variables))
vifs_ols_all[[resp_names[1]]] %>% ggplot(aes(x = VIF)) +
  geom_histogram(fill = 'grey80', binwidth = .5) +
  scale_x_continuous(breaks = seq(0, 13, by = 3)) +
  labs(x = "Explanatory Variables (Regions)",
       y = 'Count', title="Variance Inflation Factor of\nOLS Explanatory Variables")+ 
   theme_light() +
  theme(text = element_text(size = 30))

summary(vifs_ols_all[[1]]$VIF)  

```

## prepare data to plot vif, significant, se/sd and coef for OLS and elastic net

```{r}

realModelTidy <- tidy(fit_ols_all[[resp_names[1]]]) 

realModelVif <- tibble::enframe(car::vif(fit_ols_all[[resp_names[1]]])) %>% 
  rename(term = name, vif = value) 
                
realModelTidyVif <- realModelTidy %>% left_join(realModelVif, by ="term")

coefs_enet <- extract_tibble(elastic_mod = fit_enet_all_IQR[[resp_names[1]]],alpha_index = paste0("a",glmn_tuning_all_IQR[[1]]$mixture))%>% 
  mutate(type = ifelse(type == 'Null', 'Null permuted models', 'Target models'))

coefs_enetTrimmed <- coefs_enet %>% filter(type != "Null permuted models") %>% 
  rename(term = variable, eNetPval = pvalue) 

realModelTidyVifEnet <- realModelTidyVif %>% left_join(coefs_enetTrimmed, by ="term")

realModelTidyVifEnetNonTrimmed <- coefs_enet %>%   rename(term = variable, eNetPval = pvalue) %>%
   left_join(realModelTidyVif, by ="term")

coefs_enetNull <- coefs_enet %>% filter(type == "Null permuted models") %>% 
  rename(nullWmean = wmean, nullWsd = wsd, term = variable) %>% select(term, nullWmean, nullWsd)

coefs_enetTarget <- coefs_enet %>% filter(type != "Null permuted models") %>% 
  rename(targetWmean = wmean, targetWsd = wsd, term = variable,eNetPval = pvalue) %>% select(term, eNetPval, targetWmean, targetWsd)

realModelTidyVifEnetNull <- realModelTidyVif %>% left_join(coefs_enetTarget,by ="term") %>% left_join(coefs_enetNull, by ="term") 

```

## OLS SE as a funct of VIF

```{r}
ggplot(realModelTidyVifEnetNull , aes(x = vif, y = std.error, color= p.value<=.05, )) +
  geom_point(size = 5, alpha = 0.4) + 
  scale_colour_discrete(name="p value",
                         breaks=c("FALSE", "TRUE"),
                         labels=c("> .05", "< .05")) +
#  geom_linerange() +
  theme_light() +
  theme(text = element_text(size = 30)) +
  theme(legend.position="top") + 
  xlab("Variance Inflation Factor") + ylab("OLS\nStandard Error") +
  ylim(0, .05)

```

## OLS Coef ±2SE as a funct of VIF

```{r}

ggplot(realModelTidyVifEnetNull , aes(x = vif, y = estimate, color= p.value<=.05, ymin = estimate - (2 * std.error), ymax = estimate + (2 * std.error))) +
  geom_point(size = 5, alpha = 0.4) + 
  scale_colour_discrete(name="p value",
                         breaks=c("FALSE", "TRUE"),
                         labels=c("> .05", "< .05")) +
  geom_linerange() +
  theme_light() +
  theme(text = element_text(size = 30)) +
  guides(color = FALSE) +
#  theme(legend.position="top") + 
  xlab("Variance Inflation Factor") + ylab("OLS\nCoefficients ±2SE") +
  geom_hline(yintercept = 0) 

```

## Enet null SD as a funct of VIF

```{r}
realModelTidyVifEnetNull %>%
ggplot(aes(x = vif, y = nullWsd, color= p.value<=.05, )) +
  geom_point(size = 5, alpha = 0.4) + 
  scale_colour_discrete(name="p value",
                         breaks=c("FALSE", "TRUE"),
                         labels=c("> .05", "< .05")) +
#  geom_linerange() +
  theme_light() +
  theme(text = element_text(size = 30)) +
  theme(legend.position="top") + 
  xlab("Variance Inflation Factor") + ylab("Elastic Net\nSD of Permuted Null") +
  ylim(0, .021)
```

## Enet null Coef ±2SD as a funct of VIF

```{r}

ggplot(realModelTidyVifEnetNull, aes(x = vif, y = nullWmean, color= eNetPval<=.05, 
                                     ymin = nullWmean - (2 * nullWsd), ymax = nullWmean + (2 * nullWsd))) +
  geom_point(size = 5, alpha = 0.4) + 
  scale_colour_discrete(name="p value",
                         breaks=c("FALSE", "TRUE"),
                         labels=c("> .05", "< .05")) +
  geom_linerange() +
  theme_light() +
  theme(text = element_text(size = 30)) +
  guides(color = FALSE) +
  #theme(legend.position="top") + 
  xlab("Variance Inflation Factor") + ylab("Elastic Net\nCoefficients of\n Permuted Null ± 2SD") 


ggplot(realModelTidyVifEnetNonTrimmed, aes(x = vif, y = wmean, 
                                           color= eNetPval<=.05, 
                                           ymin = wmean - (2 * wsd), ymax = wmean + (2 * wsd),
                                           shape = type)) +
  geom_point(size = 5, alpha = 0.4) + 
  scale_colour_discrete(name="p value",
                         breaks=c("FALSE", "TRUE"),
                         labels=c("> .05", "< .05")) +
  scale_shape_discrete(name="",
                         breaks=c("Null permuted models", "Target models"),
                         labels=c("Null", "Target")) +
  geom_linerange() +
  theme_light() +
  theme(text = element_text(size = 30)) +
  guides(color = FALSE) +
  theme(legend.justification=c(1,0), legend.position=c(1,0)) +
  #theme(legend.position="top") + 
  xlab("Variance Inflation Factor") + ylab("Elastic Net\nCoefficients ± 2SD") 

```

# Compare significant explanatory vars across models

```{r signif, fig.height=16, fig.width=8}
signif_rois_fdr_all <- simple_all_IQR %>% map(.,~mutate(.,signif = ifelse(FDR < 0.05, 1, 0),model = 'FDR',roi = str_remove(roi, 'roi_')) %>%
  select(.,model, roi, signif)%>%
    left_join(.,new_shorter_names, by= "roi"))
  
signif_rois_bonf_all <- simple_all_IQR %>% map(.,~mutate(.,signif = ifelse(bonferroni < 0.05, 1, 0),model = 'Bonferroni',roi = str_remove(roi, 'roi_')) %>%select(.,model, roi, signif)%>%
    left_join(.,new_shorter_names, by= "roi"))

signif_rois_ols_all <-fit_ols_all %>% map(.,~broom::tidy(.) %>%filter(.,term != '(Intercept)') %>%
  mutate(.,signif = ifelse(p.value < 0.05, 1, 0),model = 'OLS',roi = str_remove(term, 'roi_')) %>%
  select(.,model, roi, signif)%>%
    left_join(.,new_shorter_names, by= "roi")) 

signif_rois_enet_all <- resp_names %>%  map(.,~extract_tibble(fit_enet_all_IQR[[.]], alpha_index = paste0("a",glmn_tuning_all_IQR[[.]]$mixture))%>%
  filter(.,type != 'Null') %>%
  mutate(.,roi = str_remove(variable, '^roi_'),signif = ifelse(pvalue < 0.05, 1, 0),model = 'Elastic net') %>%
  select(.,model, roi, signif)%>%
    left_join(.,new_shorter_names, by= "roi")) 

signif_rois_all <- resp_names %>% map(.,~bind_rows(signif_rois_fdr_all[[.]], signif_rois_bonf_all[[.]], signif_rois_ols_all[[.]], signif_rois_enet_all[[.]]) %>%mutate(.,model = factor(model, levels = c('FDR', 'Bonferroni','OLS', 'Elastic net')))) 

signif_rois_long_all <- signif_rois_all %>% map(.,~pivot_wider(.,names_from = model, values_from = signif) %>%
  filter(.,`FDR` == 1 | `Bonferroni` == 1 | `OLS` == 1 | `Elastic net` == 1) %>%
  mutate(.,n_mods = 1 * `OLS` + 2 * `Elastic net` + 4 * `Bonferroni` + 6 * `FDR`) %>% 
  pivot_longer(.,names_to = 'model', values_to = 'signif', cols = `FDR`:`Elastic net`) %>%
  mutate(.,signif = ifelse(signif == 0, 'Not significant', 'Significant'))%>%
  mutate(.,model = factor(model, levels = c('Elastic net','OLS' ,'Bonferroni', 'FDR'))) %>%
  mutate(.,facetRow4 = ifelse(row_number() <= (nrow(.)/4)+2, 'Left', 
                             ifelse(row_number() <= ((nrow(.)/4)*2), 'LeftMid',
                                    ifelse(row_number() <= ((nrow(.)/4)*3)+2, 'RightMid', 'Right')))) %>%
  mutate(.,facetRow3 = ifelse(row_number() <= nrow(.)/3, 'Left', 
                             ifelse(row_number() <= (nrow(.)/3)*2, 'Mid','Right'))) %>% 
   mutate(.,facetRow2 = ifelse(row_number() <= nrow(.)/2, 'Left', 'Right'))  
  )
```


```{r,fig.height=6, fig.width=10}
 resp_names%>% map(~ggplot(signif_rois_long_all[[.]],aes(x = fct_rev(model), y = fct_reorder(roiShort, n_mods), fill = signif)) +
  geom_tile(col = 'grey60') +
 # scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  scale_fill_manual(values = c('grey80', "#56B4E9")) +
  labs(x = '', y = 'Brain Regions', fill = '',
       title = resp_var_plotting$longer_name[[which(resp_var_plotting$response==.)]]) +
facet_wrap(~ facetRow4, scales = 'free_y', ncol= 4) +
# theme(aspect.ratio = 6) +
  theme(plot.title = element_text(size = 20)) + 
  theme(legend.position="top") +
  theme(legend.text = element_text(size = 15)) +
  theme(axis.text.x = element_text(angle = 90)) +
  theme(axis.title.y = element_text(size =15)) + 
  theme(axis.text.x = element_text(size = 10)) +
  theme(axis.text.y = element_text(size = 10)) + 
    theme(
    strip.background = element_blank(),
    strip.text.x = element_blank()))  
```

# Ploting coefs on the brain

```{r libraries}
library(ggseg)
library(ggsegExtra)
#library(ggseg3d)
library(ggsegDesterieux)
library(RColorBrewer)
library(ggpubr)
library(png)
library("cowplot")
```

## Create a dataframe using atlas' labels

```{r input_all_analysis_outputs, echo=FALSE}
data_all_listwise <- readRDS(file = "/mnt/data/Yue script/data_all_listwise.RData")
## simple regressions
simple_all <- readRDS(file ="/mnt/data/Yue script/simple_reg_all_IQR.RData" )
## OLS
fit_ols_all <- readRDS(file ="/mnt/data/Yue script/fit_ols_all_IQR.RData")
## Elastic net
fit_ridge_all  <- readRDS('/mnt/data/Yue script/fit_ridge_all_IQR.RData')
## Elastic net parameter tuning
glmn_tuning_all <- readRDS(file ="/mnt/data/Yue script/glmn_tune_all_IQR.RData")
#saveRDS(tidy_fit_enet_all, file='/mnt/data/Yue script/tidy_fit_enet_all.RData')
tidy_fit_enet_all<- readRDS(file='/mnt/data/Yue script/tidy_fit_enet_all_IQR.RData')

```

## variable names

```{r response_names}
Resp_Var <- c('TFMRI_NB_ALL_BEH_C2B_RATE',
              "NIHTBX_PICVOCAB_UNCORRECTED", 
              "NIHTBX_FLANKER_UNCORRECTED",
              "NIHTBX_LIST_UNCORRECTED",
              "NIHTBX_CARDSORT_UNCORRECTED",
              "NIHTBX_PATTERN_UNCORRECTED",
              "NIHTBX_PICTURE_UNCORRECTED",
              "NIHTBX_READING_UNCORRECTED",
              "LMT_SCR_PERC_CORRECT",
              "PEA_RAVLT_LD_TRIAL_VII_TC",
              "PEA_WISCV_TRS")
resp_var_plotting_long <- c("2-back task: percent accuracy",
  "Picture vocabulary test",
  "Flanker test",
  "List sorting working memory",
  "Dimentional change card sort test",
  "Pattern comparison processing speed test",
  "Picture sequence memory test",
  "Oral reading recognition test",
  "Little man task correct percentage",
  "RAVLT long delay trial VII total correct",
  "WISC_V matrix reasoning total raw score"
)
resp_var_plotting_short <- c("2-back Work Mem","Pic Vocab","Flanker","List Work Mem","Cog Flex","Pattern Speed","Seq Memory","Reading Recog","Little Man","Audi Verbal","Matrix Reason")
resp_var_plotting <- tibble("response" =Resp_Var, "longer_name"=resp_var_plotting_long,"short_name"=resp_var_plotting_short)

resp_names <-data_all_listwise %>% select(all_of(Resp_Var))%>%
  names()%>%
  set_names()
```

```{r ggseg, fig.show='hide'}
##data manipulation for plotting
coefs_simple_all <- simple_all %>% map(.,~mutate(.,label = str_replace_all(roi, '\\.', '-')) %>% 
  mutate(.,label = str_replace_all(label, 'roi_', '')) %>% 
  mutate(.,label = str_replace_all(label, 'Brain-Stem', 'brain-stem')) %>% 
  mutate(.,label = str_replace_all(label, 'Right-Cerebellum-Cortex
', 'right-cerebellum-cortex')) %>% 
  mutate(.,estimateFDR = ifelse(FDR <= .05, estimate, NA)) %>% 
  mutate(.,estimateBon = ifelse(bonferroni <= .05, estimate, NA)))

coefs_simple_ggsegDes_all <- vector("list", length = length(resp_names))
names(coefs_simple_ggsegDes_all)<- resp_names

for(i in 1:length(resp_names)){
  #desterieux is our subcortical atlas
coefs_simple_ggsegDes_all[[resp_names[i]]] <- desterieux %>% 
  select(label) %>% 
  na.omit() %>% 
  left_join(select(coefs_simple_all[[resp_names[i]]], label, estimate, estimateFDR, estimateBon,performance), by = "label")
}

#original aseg has both axial and sagital views. Need to filter out sagital view
aseg <- aseg %>% filter(side=="axial")

coefs_simple_ggsegAseg_all <- vector("list", length = length(resp_names))
names(coefs_simple_ggsegAseg_all)<- resp_names

for(i in 1:length(resp_names)){
#aseg is our subcortical atlas
coefs_simple_ggsegAseg_all[[resp_names[i]]] <- aseg %>% 
  select(label) %>% 
  na.omit() %>% 
  left_join(select(coefs_simple_all[[resp_names[i]]], label, estimate, estimateFDR, estimateBon,performance), by = "label")
}

estimationLimit_all <-resp_names%>% map(.,~c(range(c(coefs_simple_ggsegDes_all[[.]]$estimate,coefs_simple_ggsegAseg_all[[.]]$estimate), na.rm = TRUE))) 
performanceLimit_all <-resp_names%>% map(.,~c(range(c(coefs_simple_ggsegDes_all[[.]]$performance,coefs_simple_ggsegAseg_all[[.]]$performance), na.rm = TRUE)))  
```

## uncorrected estimates on cortical

```{r, fig.show='hide'}

estimateUncorrectedCort_all <-resp_names %>% map(.,~ggseg(.data = coefs_simple_ggsegDes_all[[.]] ,
              atlas = 'desterieux', 
              mapping = aes(fill = estimate),
 #             position = "stacked",
              colour="black"
              ) + 
              theme_void() +
              scale_fill_gradient2(limits = estimationLimit_all[[.]], midpoint = 0, low = "blue", mid = "white",
                            high = "red", space = "Lab", na.value="transparent" ) +
              theme(legend.position = "none")+
              labs(title =resp_var_plotting$longer_name[[which(resp_var_plotting$response==.)]])) 

ggpubr::ggarrange(plotlist=estimateUncorrectedCort_all,nrow=6)

```

## uncorrected estimates on subcortical

```{r, fig.show='hide'}

estimateUncorrectedSub_all <- resp_names %>% map(.,~ggseg(.data = coefs_simple_ggsegAseg_all[[.]] ,
              atlas = 'aseg', 
              mapping = aes(fill = estimate),
              view = "axial",
 #             position = "stacked",
              colour="black"
              ) + 
              theme_void() +
              scale_fill_gradient2(limits = estimationLimit_all[[.]], midpoint = 0, low = "blue", mid = "white",
                            high = "red", space = "Lab", na.value="transparent" ) +
              theme(legend.position = "none")
 #+ labs(title =resp_var_plotting$short_name[[which(resp_var_plotting$response==.)]])
 ) 
ggpubr::ggarrange(plotlist=estimateUncorrectedSub_all,nrow=3,ncol=4)


```

## FDR-ed estimates on cortical

```{r , fig.show='hide'}
estimateFDRCort_all <- resp_names %>% map(.,~ggseg(.data = coefs_simple_ggsegDes_all[[.]] ,
              atlas = 'desterieux', 
              mapping = aes(fill = estimateFDR),
#             position = "stacked",
              colour="black"
              ) + 
              theme_void() +
              scale_fill_gradient2(limits = estimationLimit_all[[.]], midpoint = 0, low = "blue", mid = "white",
                            high = "red", space = "Lab", na.value="transparent" ) +
              theme(legend.position = "none") +
              labs(title =paste0("Mass-Univariate FDR-Corrected Coefficients "))) 

ggarrange(plotlist=estimateFDRCort_all,nrow=6)

```

## FDR-ed estimates on subcortical

```{r, fig.show='hide'}

estimateFDRSub_all  <- resp_names %>% map(.,~ggseg(.data = coefs_simple_ggsegAseg_all[[.]] ,
              atlas = 'aseg', 
              mapping = aes(fill = estimateFDR),
              view = "axial",
 #             position = "stacked",
              colour="black"
              ) + 
              theme_void() +
              scale_fill_gradient2(limits = estimationLimit_all[[.]], midpoint = 0, low = "blue", mid = "white",
                            high = "red", space = "Lab", na.value="transparent" ) + 
              guides(fill = guide_colourbar(barwidth = 0.5, barheight = 3, title = NULL))
# +labs(title =resp_var_plotting$short_name[[which(resp_var_plotting$response==.)]])
 ) 
ggpubr::ggarrange(plotlist=estimateFDRSub_all,nrow=3,ncol=4,common.legend = TRUE,legend = "right")
```

## Bonferroni-ed estimates on cortical

```{r , fig.show='hide'}
estimateBonCort_all <- resp_names %>% map(.,~ggseg(.data = coefs_simple_ggsegDes_all[[.]] ,
              atlas = 'desterieux', 
              mapping = aes(fill = estimateBon),
 #             position = "stacked",
              colour="black"
              ) + 
              theme_void() +
              scale_fill_gradient2(limits = estimationLimit_all[[.]], midpoint = 0, low = "blue", mid = "white",
                            high = "red", space = "Lab", na.value="transparent" ) +
              theme(legend.position = "none") + 
              ggtitle(paste0("Mass-Univariate Bonferroni-Corrected Coefficients "))) 
ggarrange(plotlist=estimateBonCort_all,nrow=6)
```

## Bonferroni-ed estimates on subcortical

```{r , fig.show='hide'}

estimateBonSub_all <- resp_names %>% map(.,~ggseg(.data = coefs_simple_ggsegAseg_all[[.]] ,
              atlas = 'aseg', 
              mapping = aes(fill = estimateBon),
              view = "axial",
 #             position = "stacked",
              colour="black"
              ) + 
              theme_void() +
              scale_fill_gradient2(limits = estimationLimit_all[[.]], midpoint = 0, low = "blue", mid = "white",
                            high = "red", space = "Lab", na.value="transparent" ) + 
              guides(fill = guide_colourbar(barwidth = 0.5, barheight = 3, title = NULL))
 #+labs(title =resp_var_plotting$short_name[[which(resp_var_plotting$response==.)]])
 ) 
ggpubr::ggarrange(plotlist=estimateBonSub_all,nrow=3,ncol=4,common.legend = TRUE,legend = "right")
```

## predictive ability of the mass univariate on cortical

```{r ,  fig.show='hide'}
predictionCort_all <-resp_names %>% map(.,~ggseg(.data = coefs_simple_ggsegDes_all[[.]] ,
              atlas = 'desterieux', 
              mapping = aes(fill = performance),
 #             position = "stacked",
              colour="black"
              ) + 
              theme_void() +
              scale_fill_gradient2(limits = performanceLimit_all[[.]], 
                                   midpoint = 0, low = "blue", mid = "white",
                                   high = "red", space = "Lab", na.value="transparent" ) +
              theme(legend.position = "none") + 
              ggtitle(paste0("Mass-Univariate Out-Of-Sample Prediction (Pearson's r) "))) 
ggarrange(plotlist=predictionCort_all,nrow=6)
```

## prediction performance on subcortical

```{r, fig.show='hide'}

predictionSub_all <-resp_names%>%   map (.,~ggseg(.data = coefs_simple_ggsegAseg_all[[.]] ,
              atlas = 'aseg', 
              mapping = aes(fill = performance),
              view = "axial",
 #             position = "stacked",
              colour="black"
              ) + 
              theme_void() +
              scale_fill_gradient2(limits = performanceLimit_all[[.]], midpoint = 0, low = "blue", mid = "white",
                            high = "red", space = "Lab", na.value="transparent") + 
              guides(fill = guide_colourbar(barwidth = 0.5, barheight = 3, title = NULL))
#              theme(legend.position = "none")) 
)
ggpubr::ggarrange(plotlist=predictionSub_all,nrow=3,ncol=4,common.legend = TRUE,legend = "right")
```

## OLS

```{r OLS_output_manipulation , fig.show='hide'}
tidy_fit_ols_all <-fit_ols_all %>%  map(., ~broom::tidy(.)%>%
                                    filter(.,term != '(Intercept)')%>%
                                    mutate(.,label = str_replace_all(term, '\\.', '-')) %>% 
                                    mutate(.,label = str_replace_all(label, 'roi_', '')) %>% 
                                    mutate(.,label = str_replace_all(label, 'Brain-Stem', 'brain-stem')) %>% 
                                    mutate(.,label = str_replace_all(label, 'Right-Cerebellum-Cortex', 'right-cerebellum-cortex'))%>% 
                                    mutate(.,estimate_sig = ifelse(p.value <= .05, estimate, NA)) 
 )

coefs_ols_ggsegDes_all <- vector("list", length = length(resp_names))
names(coefs_ols_ggsegDes_all)<- resp_names

for(i in 1:length(resp_names)){
  #desterieux is our subcortical atlas
coefs_ols_ggsegDes_all[[resp_names[i]]] <- desterieux %>% 
  select(label) %>% 
  na.omit() %>% 
  left_join(select(tidy_fit_ols_all[[resp_names[i]]], label, estimate, estimate_sig), by = "label")
}

#original aseg has both axial and sagital views. Need to filter out sagital view
aseg <- aseg %>% filter(side=="axial")

coefs_ols_ggsegAseg_all <- vector("list", length = length(resp_names))
names(coefs_ols_ggsegAseg_all)<- resp_names

for(i in 1:length(resp_names)){
#aseg is our subcortical atlas
coefs_ols_ggsegAseg_all[[resp_names[i]]] <- aseg %>% 
  select(label) %>% 
  na.omit() %>% 
  left_join(select(tidy_fit_ols_all[[resp_names[i]]], label, estimate, estimate_sig), by = "label")
}

estimationLimit_ols_all <-resp_names%>% map(.,~c(range(c(coefs_ols_ggsegDes_all[[.]]$estimate,coefs_ols_ggsegAseg_all[[.]]$estimate), na.rm = TRUE))) 

```

```{r , fig.show='hide'}

estimateCort_ols_all <-resp_names %>% map(.,~ggseg(.data = coefs_ols_ggsegDes_all[[.]] ,
              atlas = 'desterieux', 
              mapping = aes(fill = estimate_sig),
 #             position = "stacked",
              colour="black"
              ) + 
              theme_void() +
              scale_fill_gradient2(limits = estimationLimit_ols_all[[.]], midpoint = 0, low = "blue", mid = "white",
                            high = "red", space = "Lab", na.value="transparent" ) +
              theme(legend.position = "none")+
              labs(title =paste0("OLS Coefficients ")) )

ggpubr::ggarrange(plotlist=estimateCort_ols_all,nrow=6)
```

```{r , fig.show='hide'}

estimateSub_ols_all <- resp_names %>% map(.,~ggseg(.data = coefs_ols_ggsegAseg_all[[.]] ,
              atlas = 'aseg', 
              mapping = aes(fill = estimate_sig),
              view = "axial",
 #             position = "stacked",
              colour="black"
              ) + 
              theme_void() +
              scale_fill_gradient2(limits = estimationLimit_ols_all[[.]], midpoint = 0, low = "blue", mid = "white",
                            high = "red", space = "Lab", na.value="transparent" ) + 
              guides(fill = guide_colourbar(barwidth = 0.5, barheight = 3, title = NULL))
 #+labs(title =resp_var_plotting$short_name[[which(resp_var_plotting$response==.)]])
 ) 
ggpubr::ggarrange(plotlist=estimateSub_ols_all,nrow=3,ncol=4,common.legend = TRUE,legend = "right")
```

## Elastic net

```{r, fig.show='hide'}
tidy_fit_enet_all <- vector("list", length = length(resp_names))
names(tidy_fit_enet_all)<- resp_names

for(i in 1: length(resp_names)){
  elastic_mod=fit_ridge_all[[resp_names[i]]]
  alpha_index = paste0("a",glmn_tuning_all[[resp_names[i]]]$mixture)
  variable <- elastic_mod$feature_coef_wmean[, alpha_index] %>% names()
    wmean <- as.numeric(elastic_mod$feature_coef_wmean[, alpha_index])  
    pvalue <- as.numeric(elastic_mod$feature_coef_model_vs_null_pval[, alpha_index]) 
    tib <- tibble::tibble(variable, wmean, pvalue)
    tidy_fit_enet_all[[resp_names[i]]]<- tib}
```


```{r, fig.show='hide'}
tidy_fit_enet_all <-tidy_fit_enet_all %>%  map(., ~mutate(.,label = str_replace_all(variable, '\\.', '-')) %>% 
                                    mutate(.,label = str_replace_all(label, 'roi_', '')) %>% 
                                    mutate(.,label = str_replace_all(label, 'Brain-Stem', 'brain-stem')) %>% 
                                    mutate(.,label = str_replace_all(label, 'Right-Cerebellum-Cortex', 'right-cerebellum-cortex'))%>% 
                                    mutate(.,estimate_sig = ifelse(pvalue <= .05, wmean, NA)))
```


```{r, fig.show='hide'}
coefs_enet_ggsegDes_all <- vector("list", length = length(resp_names))
names(coefs_enet_ggsegDes_all)<- resp_names

for(i in 1:length(resp_names)){
  #desterieux is our subcortical atlas
coefs_enet_ggsegDes_all[[resp_names[i]]] <- desterieux %>% 
  select(label) %>% 
  na.omit() %>% 
  left_join(select(tidy_fit_enet_all[[resp_names[i]]], label, wmean, estimate_sig), by = "label")
}

#original aseg has both axial and sagital views. Need to filter out sagital view
aseg <- aseg %>% filter(side=="axial")

coefs_enet_ggsegAseg_all <- vector("list", length = length(resp_names))
names(coefs_enet_ggsegAseg_all)<- resp_names

for(i in 1:length(resp_names)){
#aseg is our subcortical atlas
coefs_enet_ggsegAseg_all[[resp_names[i]]] <- aseg %>% 
  select(label) %>% 
  na.omit() %>% 
  left_join(select(tidy_fit_enet_all[[resp_names[i]]], label, wmean, estimate_sig), by = "label")
}

estimationLimit_enet_all <-resp_names%>% map(.,~c(range(c(coefs_enet_ggsegDes_all[[.]]$wmean,coefs_enet_ggsegAseg_all[[.]]$wmean), na.rm = TRUE))) 
```

```{r, fig.show='hide'}

estimateCort_enet_all <-resp_names %>% map(.,~ggseg(.data = coefs_enet_ggsegDes_all[[.]] ,
              atlas = 'desterieux', 
              mapping = aes(fill = estimate_sig),
 #             position = "stacked",
              colour="black"
              ) + 
              theme_void() +
              scale_fill_gradient2(limits = estimationLimit_enet_all[[.]], midpoint = 0, low = "blue", mid = "white",
                            high = "red", space = "Lab", na.value="transparent" ) +
              theme(legend.position = "none")+
              labs(title =paste0("Elastic Net Coefficients ")) )

ggpubr::ggarrange(plotlist=estimateCort_enet_all,nrow=6)
```


```{r, fig.show='hide'}

estimateSub_enet_all <- resp_names %>% map(.,~ggseg(.data = coefs_enet_ggsegAseg_all[[.]] ,
              atlas = 'aseg', 
              mapping = aes(fill = estimate_sig),
              view = "axial",
 #             position = "stacked",
              colour="black"
              ) + 
              theme_void() +
              scale_fill_gradient2(limits = estimationLimit_enet_all[[.]], midpoint = 0, low = "blue", mid = "white",
                            high = "red", space = "Lab", na.value="transparent" ) + 
              guides(fill = guide_colourbar(barwidth = 0.5, barheight = 3, title = NULL))
 #+labs(title =resp_var_plotting$short_name[[which(resp_var_plotting$response==.)]])
 ) 
ggpubr::ggarrange(plotlist=estimateSub_enet_all,nrow=3,ncol=4,common.legend = TRUE,legend = "right")
```

## Combine all of the methods  

```{r, echo=FALSE, fig.align = "center", fig.height = 7, fig.width = 7}
library("grid")
library("gridExtra")


resp_names %>% map(.,~gridExtra::grid.arrange(estimateFDRCort_all[[.]], estimateFDRSub_all[[.]], 
                        estimateBonCort_all[[.]], estimateBonSub_all[[.]], 
                        predictionCort_all[[.]], predictionSub_all[[.]],
                        estimateCort_ols_all[[.]],estimateSub_ols_all[[.]],
                        estimateCort_enet_all[[.]],estimateSub_enet_all[[.]],
                        nrow = 5, ncol = 2,
                        widths  = c(4, 1.5), 
                        heights=unit(c(1.1,1.1,1.1,1.1,1.1), c("in","in", "in", "in","in")),
                        top = textGrob(resp_var_plotting$longer_name[[which(resp_var_plotting$response==.)]],
                                       gp=gpar(fontsize=20,font=3),
                                       hjust=0,x=0)))
```

# R session and library
```{r}

pander::pander(sessionInfo())

```
